%!TEX root = thesis.tex

\chapter{Conclusions}
\label{chapter:conclusions}

This master's thesis presented a proposal and implementation of automated acceptance testing environment for payment terminal software and addressed the theories and problems related to the topic. Presented AAT environment was joint combination of open source hardware and software and was formed by the requirements of Eficode Oy's customer. AAT environment presented in this thesis was able to fulfill the requirement of automating a majority of the software testing of the payment terminals which was previously done manually.

Literature review of this master's thesis addressed the four problem statements introduced in the beginning of this master's thesis. Research questions were also discussed and suggestions for future research were presented in Chapter~\ref{chapter:discussion} after the implemented AAT was introduced in previous Chapters.

Presented architecture and testing solution proved to be adaptive to different kinds of payment terminals and also enabled testing of three different payment terminals in parallel setup to reduce the overall duration of the acceptance testing process. Solution also provided transparency to the users and developers of the security critical system under testing. As a result of this project, an open source Robot Framework library was also published for controlling any kinds of robots supporting serial communication and G-code commands.

This master's thesis also lays a promise of how commonly and inexpensively available components can be used in demanding applications. By combining different open source products, highly adaptive AAT environment was created for the needs of automated acceptance testing of payment terminal software successfully.